\vspace{-5em}\Huge Generation of a Synthetic Population and Travel Network for an Agent Based Traffic Simulation

### 2023-08-04 paper/paper.tex
paper update

\quad Traffic modeling requires various inputs to accurately simulate a real world scenario. This paper takes a look at how to generate traffic demand for agent based models in particular. By taking a set of configurations from a user, the proposed program stochastically produces a population as well as the network of a city. This data is then converted into a format that can be simulated and tested via agent-based models. Thus, researchers can analyze the effect of various attributes of a road network on the traffic produced within it. With further modifications and enhancements, this software can also study the effects of different types of vehicles on carbon emissions. These improvements, as well as furthering multi-modal transportation are also discussed in this paper.

@@

\begin{multicols}{2}
    \section{Introduction}
    \quad Although agent-based modeling has become increasingly popular in recent years, traffic simulations have existed for much longer. Previously, aggregate four-step models were the primary tool utilized. These systems did not capture the emergent effects of interactions between agents, and many did not even analyze the diversity of activities in each individual's schedules \cite{types-of-modeling}. Intuitively, this leads to several problems. First off, the lack of specific detail taken into account by these models results in simulations that simply predict patterns of groups of people. Multi-modal transportation is not captured very well in these cases. In addition, these models also don't work well with the variety of activities of different people in a population, thus they are limited by aggregate data as a whole. \\

@@

    \subsection{Zoning} \label{zoning}
    \quad When it comes to zoning, it is first crucial to understand the different types of zoning policies and their implementations in a city. First off, one of the most popular types of zoning is Euclidean zoning, which came to be known as such after its controversial use in Euclid, Ohio \cite{zoning}. This form of zoning consists of rigid divisions between types of buildings in various regions of a city. For example, residential property would be separated from commercial or industrial centers. The reasoning behind this is essentially to protect quality of living and ensure standards of health are followed. However, due to its rigid structure, the cities with heavy Euclidean zoning suffer from urban sprawl, where parts of the city continue to grow outwards. Still, within Euclidean zoning there are two variations that work differently. Hierarchical Euclidean zoning is a policy that allows for these rigid zones to be stacked upon one another. This allows for apartment complexes, for example, to exist within commercial or industrial centers. Flat zoning, on the other hand, is a standard implementation of Euclidean zoning that enforces strictly one purpose for each division of land.\\

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.4\textwidth]{images/depthfirstsearch.jpg}
        \caption{Example graph with steps of depth first search \cite{depthfirstsearch}}
        \label{fig:depth-first-search}
    \end{figure}

@@

>>>>

\quad Traffic modeling requires various inputs to accurately simulate a real world scenario. Most traffic demand synthesis models are based on real world data, and do not reveal much information about the effects of specific attributes in cities on their traffic. By taking a set of configurations from a user, the proposed program stochastically produces a population as well as the network of a city. The program allows researchers to analyze the broad effects of city design on traffic flow, which will allow for city engineers to gain a broad understanding of how people will behave within the networks they create. With further modifications and enhancements, this software can also study the effects of different types of vehicles on carbon emissions. A possible wrapper stochastic approximation model could also determine better configurations of a given city design by interacting with this program.

@@

\begin{multicols}{2}
    \section{Introduction}
    \quad Although agent-based modeling has become increasingly popular in recent years, traffic simulations have existed for much longer. Previously, aggregate four-step models were the primary tool utilized. These models took general data of the flow of populations between zones and utilized predictive analysis techniques to determine traffic flows of the future. The main problem with this was that the models did not capture emergent effects of interactions between agents \cite{types-of-modeling}. Intuitively, this leads to several problems. First off, the lack of specific detail taken into account by these models results in simulations that simply predict patterns of groups of people. Multi-modal transportation is not captured very well in these cases. In addition, these models also don't work well with the variety of activities of different people in a population, thus they are limited by aggregate data as a whole. \\

@@

    \subsection{Zoning} \label{zoning}

    \quad When it comes to zoning, it is first crucial to understand the different types of zoning policies and their implementations in a city. First off, one of the most popular types of zoning is Euclidean zoning, which came to be known as such after its controversial use in Euclid, Ohio \cite{zoning}. This form of zoning consists of rigid divisions between types of buildings in various regions of a city. For example, residential property would be separated from commercial or industrial centers. The reasoning behind this is essentially to protect quality of living and ensure standards of health are followed. However, due to its rigid structure, the cities with heavy Euclidean zoning suffer from urban sprawl, where parts of the city continue to grow outwards. Still, within Euclidean zoning there are two variations that work differently. Hierarchical Euclidean zoning is a policy that allows for these rigid zones to be stacked upon one another. This allows for apartment complexes, for example, to exist within commercial or industrial centers. Flat zoning, on the other hand, is a standard implementation of Euclidean zoning that enforces strictly one purpose for each division of land.\\

@@

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.45\textwidth]{images/depthfirstsearch.jpg}
        \caption{Example graph with steps of depth first search \cite{depthfirstsearch}}
        \label{fig:depth-first-search}
    \end{figure}
